Black swans in ecological time series\\ Black swans in population dynamics\\ Heavy-tailed ecological time series\\ Black swans in ecological dynamics\\ Black swan ecological dynamics\\ \ldots

### 2014-11-10 text/supp.tex
Whoops - mistake in equation
Edits to supp.tex

\item We removed GPDD Main IDs \texttt{20531} and \texttt{10139}, which we noticed were duplicates of \texttt{20579} (a heron population). \texttt{20579} contained additional years of data not present in \texttt{10139}. We removed a limited number of populations from class Angiospermopsida and Bacillariophyceae to focus the taxonomy in our analysis. We also removed any populations with an \texttt{Unknown} taxonomic class.

\item Finally, we removed populations with the following GPDD Main IDs, which we discovered data entry errors when verifying the populations with suspected black swans: \texttt{1207} because 1957 was entered as 2 but should have been 27 \citep{kendeigh1982}, \texttt{6531} because 1978 was entered as 7 should have been 47 \citep{minot1986}, and \texttt{6566} because the data did not match the graph \citep{heessen1996}.

@@

\noindent
We provide a supplemental figure of all the time series included in our analysis and indicate which values were interpolated (\percImputedPops\% of populations had at least one point interpolated also only \percImputedPoints\% of the total observations were interpolated) (Fig.~\ref{fig:all-ts}). Note that interpolation is highly unlikely to lead to black-swan detections, since black swans involve extreme increases or decreases. Table~\ref{tab:stats} shows the final taxonomic breakdown and the number of populations with interpolated values.

@@

\begin{align*}
\mathrm{Pr}(\nu_i < 0.5) &\sim \mathrm{Beta}(A_i, B_i)\\
\mu_i &= \mathrm{logit}^{-1}(\alpha
  + \alpha^\mathrm{class}_{j[i]}
  + \alpha^\mathrm{order}_{k[i]}
  + \alpha^\mathrm{species}_{l[i]}
  + X_i \beta),
  \: \text{for } i = 1, \dots, 617\\
A_i &= \phi_\mathrm{disp} \mu_i\\
B_i &= \phi_\mathrm{disp} (1 - \mu_i)\\
\alpha^\mathrm{class}_j &\sim
  \mathrm{Normal}(0, \sigma^2_{\alpha \; \mathrm{class}}),
  \: \text{for } j = 1, \dots, 6\\
\alpha^\mathrm{order}_k &\sim
  \mathrm{Normal}(0, \sigma^2_{\alpha \; \mathrm{order}}),
  \: \text{for } k = 1, \dots, 38\\
\alpha^\mathrm{species}_l &\sim
  \mathrm{Normal}(0, \sigma^2_{\alpha \; \mathrm{species}}),
  \: \text{for } l = 1, \dots, 301,
\end{align*}
where $A$ and $B$ represent the beta distribution shape parameters; $\mu_i$ represents the predicted value for population $i$, class $j$, order $k$, and species $l$; $\phi_\mathrm{disp}$ represents the dispersion parameter; and $X_i$ represents a vector of predictors (such as lifespan) for population $i$ with associated $\beta$ coefficients. The intercepts are allowed to vary from the overall intercept $\alpha$ by taxonomic class ($\alpha^\mathrm{class}_j$), taxonomic order ($\alpha^\mathrm{order}_k$), and species ($\alpha^\mathrm{species}_l$) with standard deviations $\sigma_{\alpha \; \mathrm{class}}$, $\sigma_{\alpha \; \mathrm{order}}$, and $\sigma_{\alpha \; \mathrm{species}}$. Where possible, we also allowed for error distributions around the predictors by incorporating the standard deviation of the posterior samples for the Gompertz parameters $\lambda$, $b$, and $\log \sigma$ around the mean point value as normal distributions (not shown in the above equation).

>>>>

\item We removed GPDD Main IDs \texttt{20531} and \texttt{10139}, which we noticed were duplicates of \texttt{20579} (a heron population). \texttt{20579} contained additional years of data not present in \texttt{10139}. We removed a limited number of populations from class Angiospermopsida and Bacillariophyceae to focus the taxonomy in our analysis on animals. We also removed any populations with an \texttt{Unknown} taxonomic class.

\item Finally, we removed populations with the following GPDD Main IDs, which we discovered data entry errors when verifying the populations with suspected black swans: \texttt{1207} because the 1957 data point was entered as 2 but should have been 27 \citep{kendeigh1982}, \texttt{6531} because the 1978 data point was entered as 7 should have been 47 \citep{minot1986}, and \texttt{6566} because some of the data did not match the graph \citep{heessen1996}.

@@

\noindent
We provide a supplemental figure of all the time series included in our analysis and indicate which values were interpolated (non-zero interpolations) (\percImputedPops\% of populations had at least one point interpolated but only \percImputedPoints\% of the total observations were interpolated) (Fig.~\ref{fig:all-ts}). Note that interpolation is highly unlikely to lead to black-swan detections, since black swans involve extreme increases or decreases. Table~\ref{tab:stats} shows the final taxonomic breakdown and the number of populations with interpolated values.

@@

\begin{align*}
\mathrm{Pr}(\nu_i < 10) &\sim \mathrm{Beta}(A_i, B_i)\\
\mu_i &= \mathrm{logit}^{-1}(\alpha
  + \alpha^\mathrm{class}_{j[i]}
  + \alpha^\mathrm{order}_{k[i]}
  + \alpha^\mathrm{species}_{l[i]}
  + X_i \beta),
  \: \text{for } i = 1, \dots, 617\\
A_i &= \phi_\mathrm{disp} \mu_i\\
B_i &= \phi_\mathrm{disp} (1 - \mu_i)\\
\alpha^\mathrm{class}_j &\sim
  \mathrm{Normal}(0, \sigma^2_{\alpha \; \mathrm{class}}),
  \: \text{for } j = 1, \dots, 6\\
\alpha^\mathrm{order}_k &\sim
  \mathrm{Normal}(0, \sigma^2_{\alpha \; \mathrm{order}}),
  \: \text{for } k = 1, \dots, 38\\
\alpha^\mathrm{species}_l &\sim
  \mathrm{Normal}(0, \sigma^2_{\alpha \; \mathrm{species}}),
  \: \text{for } l = 1, \dots, 301,
\end{align*}
where $A$ and $B$ represent the beta distribution shape parameters; $\mu_i$ represents the predicted value for population $i$, class $j$, order $k$, and species $l$; $\phi_\mathrm{disp}$ represents the dispersion parameter; and $X_i$ represents a vector of predictors (such as lifespan) for population $i$ with associated $\beta$ coefficients. The intercepts are allowed to vary from the overall intercept $\alpha$ by taxonomic class ($\alpha^\mathrm{class}_j$), taxonomic order ($\alpha^\mathrm{order}_k$), and species ($\alpha^\mathrm{species}_l$) with standard deviations $\sigma_{\alpha \; \mathrm{class}}$, $\sigma_{\alpha \; \mathrm{order}}$, and $\sigma_{\alpha \; \mathrm{species}}$. Where possible, we also allowed for error distributions around the predictors by incorporating the standard deviation of the posterior samples for the Gompertz parameters $\lambda$, $b$, and $\log \sigma$ around the mean point value as normal distributions (not shown in the above equation).
